Paper 1 Analysis

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New sigma resample graph.

<<resample_graph_delta_delta_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\delta$ and $\\delta_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
                    facet_formula=~Country, alpha=0.05, size = 1,
                    orig_color="black") +
  scale_x_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
  scale_y_continuous(limits=c(0,1), breaks=c(0, 0.5, 1)) +
  labs(x=expression(delta[1]), y=expression(delta))

>>>>

<<resample_graph_delta_delta_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\delta$ and $\\delta_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
                    facet_formula=~Country, alpha=0.05, size = 1,
                    orig_color="black") +
  scale_x_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
  scale_y_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
  labs(x=expression(delta[1]), y=expression(delta))

<<resample_graph_sigma_sigma_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma$ and $\\sigma_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(sigma_1, sigma), 
                    facet_formula=~Country, alpha=0.05, size = 1,
                    orig_color="black") +
  scale_x_continuous(limits=c(0, 3)) +
  scale_y_continuous(limits=c(0, 3)) +
  labs(x=expression(sigma[1]), y=expression(sigma))
